{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-10-06 thesis/thesis.tex
future - generalize from k,n; combine test case and verif sects
update fonts so charter in mathmode too
update acks

\usepackage{fontspec}
\usepackage{xeCJK}

\setmainfont{XCharter}
%\setmainfont{Utopia}[
%	Path = ./fonts/,
%	UprightFont = UtopiaStd-Regular.otf,
%	BoldFont = UtopiaStd-Semibold.otf,
%	ItalicFont = UtopiaStd-Italic.otf,
%	BoldItalicFont = UtopiaStd-SemiboldIt.otf
%	]

@@

Professor Garth Gibson is largely responsible for shaping me into the researcher I am today.
%Thanks to Garth's guidance,
%this thesis has grown into something that past-me,
%first starting research with the simple vision ``make a better autograder for 410'',
%could not have then imagined.
Despite having primary research interests in other fields,
Garth enthusiastically took on the project,
and always pushed me to explore new problem domains,
to design scientifically thorough experiments,
to write prose explaining difficult concepts approachably,
to appreciate related work as charitably as possible,
and to seek guidance from industry people with relevant experience,
despite my often stubborn refusal to leave my little comfort zone.
So, even when it took me sending 10+ email reminders to get your attention,
truly,
thanks for everything, Garth.

Professor David Eckhardt
provided unending guidance on education, writing, life, you name it,
helped revise each semester's iteration of the recruiting lecture with a keen eye for the student mind,
contributed substantially to the design of the survey,
and supplied constant enthusiasm and reassurance that Landslide was a boon to 15-410 that kept me going.
I can't express the depth of my gratitude to Dave strongly enough,
even though three of the Landslide-friendly tests never made it upstream into the official P2 test suite.

@@

@@

Many others have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Filardo were Landslide's first users besides myself back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in Chapter~\ref{chap:background}.
Professor Brandon Lucia provided valuable comments and revisions to Chapter~\ref{chap:quicksand}'s content
that ultimately led to its publication at OOPSLA 2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped greatly to improve Landslide's stability and robustness for use beyond CMU's walls,
greatly enriching Chapter~\ref{chap:education}'s evaluation.
David Blum and Skye Toor provided invaluable advice on statistical analysis
that helped me evaluate the student grade distributions therein.
Mario Dehesa-Azuara generously contributed the transactional memory data structures
that make up about half of Chapter~\ref{chap:tm}'s evaluation suite.

@@

The community of 15-410 TAs,
having surrounded me pretty much since starting undergrad,
nurtured my love of teaching
well before taking the class myself and well after graduation.
As skilled as the instructor is,
15-410 could not be the world's best operating systems class
without TAs who value thorough grading, the Socratic method,
and empathy to struggling students as much
from year to year as the crew I have known.
It was a blessing to serve, and later do research, among you all.
I am also grateful to Adam Blank and Miriam Zimmerman
for founding and organizing the class Great Practical Ideas,
which teaches oft-neglected programming skills such as version control and debugging,
which I had the opportunity to teach as head instructor one semester.

I thank the Parallel Data Lab, my research group at CMU,
for supporting me at the PDL retreat every fall,
pushing me to refine my presentation skills and to network with strangers (now familiar faces) from industry.
I also thank the retreat's industry attendees from each of the PDL Consortium member companies
for their interest even in more theoretical work
and the enlightening conversations resulting therefrom.
I thank everyone outside my immediate research circle who,
whether at the retreat or otherwise,
told me how cool they thought my research was for directly helping students --
every such reminder helped me keep my head up during darker times.

@@

Lastly,
the Android: Netrunner community has been such an important part of my life
for nearly as long as I've been a grad student.
Netrunner is a tabletop strategy deckbuilding card game
that depicts cyberspace hacking battles (completely different from real-life computer security)
alongside dystopian social issues (some of which seem oddly more familiar with each passing year).
Its characters have a diversity of ethnicity, gender identity, and sexual orientation
unparalleled in any other game I know of,
and the community that has grown around it reflects those values.
I thank in particular the other Stimhack moderators,
the members of {\sf \#rainbow-coalition},
and the local Pittsburgh crew
for their support and encouragement
and friendships very real and deep, even when forged only in text,
%\footnote{and Slack emojis},
that I hope will long outlive the silly card game that brought us together.
%It'd be an injustice to list only a few names here and omit others, but you know who you are.

@@

>>>>

%\usepackage{fontspec}
\usepackage{mathspec}
\usepackage{xeCJK}

%\setmainfont{XCharter}
\setallmainfonts(Digits,Latin){XCharter}
%\setmainfont{Utopia}[
%	Path = ./fonts/,
%	UprightFont = UtopiaStd-Regular.otf,
%	BoldFont = UtopiaStd-Semibold.otf,
%	ItalicFont = UtopiaStd-Italic.otf,
%	BoldItalicFont = UtopiaStd-SemiboldIt.otf
%	]

@@

Professor Garth Gibson is largely responsible for shaping me into the researcher I am today.
%Thanks to Garth's guidance,
%this thesis has grown into something that past-me,
%first starting research with the simple vision ``make a better autograder for 410'',
%could not have then imagined.
Despite having primary research interests in other fields,
Garth enthusiastically took on the project,
and always pushed me to explore new problem domains,
to design scientifically thorough experiments,
to explain difficult concepts approachably,
to appreciate related work as charitably as possible,
and to seek guidance from industry people with relevant experience,
despite my often stubborn refusal to leave my little comfort zone.
So, even when it took me sending 10+ email reminders to get your attention,
truly,
thanks for everything, Garth.

Professor David Eckhardt
provided unending guidance on education, writing, career, life, you name it,
helped revise each semester's iteration of the recruiting lecture with a keen eye for the student mind,
contributed substantially to the design of the survey,
and supplied constant enthusiasm and encouragement that Landslide was a boon to 15-410.
I can't express my gratitude to Dave strongly enough,
even if it took until just this week for half of the Landslide-friendly tests to be included in the official P2 test suite.
%even though three of the Landslide-friendly tests never made it upstream into the official P2 test suite.

@@

{Many others have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Filardo were Landslide's first users besides myself back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in Chapter~\ref{chap:background}.
Professor Brandon Lucia provided valuable comments and revisions to Chapter~\ref{chap:quicksand}'s content
that ultimately led to its publication at OOPSLA 2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped greatly to improve Landslide's stability and robustness for use beyond CMU's walls,
greatly enriching Chapter~\ref{chap:education}'s evaluation.
David Blum and Skye Toor provided
invaluable advice on statistical analysis
that helped me evaluate the student
% justify last line bc of manual page break
\unskip\parfillskip 0pt \par}

@@

\noindent
grade distributions therein.
Mario Dehesa-Azuara generously contributed the
transactional memory data structures
that make up about half of Chapter~\ref{chap:tm}'s evaluation suite.

Most importantly of all, I thank every student who ever used Landslide.
Though the introduction section may say differently,
their smiles and gratitude were the true motivation of this thesis.

@@

The community of 15-410 TAs,
having surrounded me pretty much since starting undergrad,
nurtured my love of teaching
well before taking the class myself and well after graduation.
As skilled as the instructor is,
15-410 could not be the world's best operating systems class
without TAs who value thorough grading, the Socratic method,
and empathy to struggling students as much
from year to year as the crew I have known.
It was a blessing to serve, and later do research, among you all.
Thanks also to Wind River for generously providing CMU with Simics educational licenses.
I am also grateful to Adam Blank and Miriam Zimmerman
for founding and organizing the class Great Practical Ideas,
which teaches oft-neglected programming skills such as version control and debugging,
which I had the opportunity to teach as head instructor one semester.

I thank the Parallel Data Lab, my research group at CMU,
for supporting me at the PDL retreat every fall,
pushing me to refine my presentation skills and to network with strangers (now familiar faces) from industry.
I also thank those industry attendees from each of the PDL Consortium member companies
for their interest, even in more theoretical work,
and the enlightening conversations resulting therefrom.
I thank everyone outside my immediate research circle who,
whether at the retreat or otherwise,
insisted how cool my research was for directly helping students --
every such reminder helped me keep my head up during darker times.

@@

Lastly,
the Android: Netrunner community has been such an important part of my life
for nearly as long as I've been a grad student.
Netrunner is a tabletop strategy deckbuilding card game
that depicts cyberspace hacking battles (completely different from real-life computer security)
alongside dystopian social issues (some of which seem oddly more familiar with each passing year).
Its characters have a diversity of ethnicity, gender identity, and sexual orientation
unparalleled in any other game I know of,
and the community that has grown around it reflects those values.
I thank in particular the other Stimhack moderators,
the members of {\sf \#rainbow-coalition},
and the local Pittsburgh crew
for their support and encouragement
and friendships very real and deep, even when forged only in text,
%\footnote{and Slack emojis},
that will long outlive the silly card game that brought us together.
%It'd be an injustice to list only a few names here and omit others, but you know who you are.

@@

\newcommand\revision[1]{#1\xspace}
